Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-06 sections/appendix.tex
cool

>>>>

\section{Mask Images}
We interpreted the following images from ``Digital Image Processing'' \cite{gonzalez_digital_2006} as masks:

\textbf{FigP1012.png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP1012.png}}

\textbf{Fig1008(a)(step edge).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1008(a)(step edge).png}}

\textbf{FigP0905(d).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(d).png}}

\textbf{FigP0528(c)(doughnut).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0528(c)(doughnut).png}}

\textbf{FigP0616(b).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0616(b).png}}

\textbf{Fig0114(c)(bottles).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0114(c)(bottles).png}}

\textbf{FigP0616(c).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0616(c).png}}

\textbf{FigP0433(b).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0433(b).png}}

\textbf{Figp0917.png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Figp0917.png}}

\textbf{FigP0905(b).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(b).png}}

\textbf{Fig1059(c)(NegADI).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1059(c)(NegADI).png}}

\textbf{Fig1111(a)(triangle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1111(a)(triangle).png}}

\textbf{Fig1111(b)(square).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1111(b)(square).png}}

\textbf{FigP0905(top).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(top).png}}

\textbf{FigP1110.png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP1110.png}}

\textbf{Fig0533(a)(circle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0533(a)(circle).png}}

\textbf{FigP0917(noisy\_rectangle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0917(noisy\_rectangle).png}}

\textbf{Fig0230(b)(dental\_xray\_mask).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0230(b)(dental\_xray\_mask).png}}

\textbf{FigP0528(b)(two\_dots).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0528(b)(two\_dots).png}}

\textbf{Fig1059(a)(AbsADI).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1059(a)(AbsADI).png}}

\textbf{Fig1059(b)(PosADI).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1059(b)(PosADI).png}}

\textbf{Fig0539(c)(shepp-logan\_phantom).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0539(c)(shepp-logan\_phantom).png}}

\textbf{FigP0905(c).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(c).png}}

\textbf{Fig1043(a)(yeast\_USC).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1043(a)(yeast\_USC).png}}

\textbf{FigP0905(U).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(U).png}}

\textbf{Fig0524(b)(blurred-impulse).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0524(b)(blurred-impulse).png}}

\textbf{Fig0424(a)(rectangle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0424(a)(rectangle).png}}

\textbf{Fig1008(c)(roof\_edge).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1008(c)(roof\_edge).png}}

\textbf{Fig0539(a)(vertical\_rectangle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0539(a)(vertical\_rectangle).png}}

\textbf{FigP0905(a).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0905(a).png}}

\textbf{FigP0433(a).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0433(a).png}}

\textbf{Fig0.15(a)(translated\_rectangle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0425(a)(translated\_rectangle).png}}

\textbf{FigP0918(c).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0918(c).png}}

\textbf{Fig0524(a)(impulse).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0524(a)(impulse).png}}

\textbf{Fig0236(a)(letter\_T).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0236(a)(letter\_T).png}}

\textbf{Fig0503 (original\_pattern).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0503 (original\_pattern).png}}

\textbf{FigP0501.png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0501.png}}

\textbf{Fig1218(airplanes).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig1218(airplanes).png}}

\textbf{Fig0534(a)(ellipse\_and\_circle).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/Fig0534(a)(ellipse\_and\_circle).png}}

\textbf{FigP0616(a).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0616(a).png}}

\textbf{FigP0918(b).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0918(b).png}}

\textbf{FigP0528(c).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0528(c).png}}

\textbf{FigP0528(a)(single\_dot).png}

\includegraphics[scale=0.15]{{./dip3e\_masks/FigP0528(a)(single\_dot).png}}
